---
title: "Hypothesis test"
output: pdf_document
date: "2023-10-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Green Lab


**Import data**

```{r}
data0 = read.table("/Users/suecai/Desktop/Green Lab/combined.txt", header = TRUE)
head(data0)
```
*Prepare data*

```{r echo=FALSE}
chrome_off = data0[data0$browser == "chrome"&data0$notification_status == "off",]
chrome_on = data0[data0$browser == "chrome"&data0$notification_status == "on",]
firefox_off = data0[data0$browser == "firefox"&data0$notification_status == "off",]
firefox_on = data0[data0$browser == "firefox"&data0$notification_status == "on",]
```

**RQ-1: Notification status**

*Normality check*

For chrome:

```{r}
par(mfrow=c(1,2)) # two plots in one row next to each other
hist(chrome_on$Energy_trapz.J., main = "Histogram of chrome-on" )
qqnorm(chrome_on$Energy_trapz.J.,  main = "Q-Q plot of chrome-on")
shapiro.test(chrome_on$Energy_trapz.J.) # check the data normality of differences of notification on 
hist(chrome_off$Energy_trapz.J. , main = "Histogram of chrome-off")
qqnorm(chrome_off$Energy_trapz.J., , main = "Q-Q plot of chrome-off")
shapiro.test(chrome_off$Energy_trapz.J.) # check the data normality of differences of notification on 
```

For firefox:

```{r}
par(mfrow=c(1,2)) # two plots in one row next to each other
hist(firefox_on$Energy_trapz.J., main = "Histogram of firefox-on" )
qqnorm(firefox_on$Energy_trapz.J.,  main = "Q-Q plot of firefox-on")
shapiro.test(firefox_on$Energy_trapz.J.) # check the data normality when notification is on under Firefox
hist(firefox_off$Energy_trapz.J. , main = "Histogram of firefox-off")
qqnorm(firefox_off$Energy_trapz.J., , main = "Q-Q plot of firefox-off")
shapiro.test(firefox_off$Energy_trapz.J.) # check the data normality when notification off under Firefox
```

Data is not normal, hence use Wilcoxon Signed-Rank Test to conduct the hypothesis test, because these two data sets are paired.

*Hypothesis test*

```{r}
wilcox.test(chrome_off$Energy_trapz.J., chrome_on$Energy_trapz.J., paired = TRUE, alternative = "less") # chrome
wilcox.test(firefox_off$Energy_trapz.J., firefox_on$Energy_trapz.J., paired = TRUE, alternative = "less") # Firefox
```

P-values are less than $0.05$, then reject $H_0$ which means the energy consumption is greater when the notification is on.

**RQ1-1: Impact of Browsers**

*Normality check*

```{r}
dif_chr = chrome_on$Energy_trapz.J. - chrome_off$Energy_trapz.J. 
dif_fire = firefox_on$Energy_trapz.J. - firefox_off$Energy_trapz.J. # Calculation of the increase in energy consumption due to switching on notifications
par(mfrow=c(1,2)) # two plots in one row next to each other
hist(dif_chr, main = "Histogram of increasing energy in chrome" )
qqnorm(dif_chr,  main = "Q-Q plot of increasing energy in chrome")
shapiro.test(dif_chr) 
hist(dif_fire, main = "Histogram of increasing energy in Firefox")
qqnorm(dif_fire , main = "Q-Q plot of increasing energy in Firefox")
shapiro.test(dif_fire) 
```

Data is not normal distributed. Hence use Mann-Whitney U Test, because these two data sets are independent.

*Hypothesis test*

```{r}
wilcox.test(dif_chr, dif_fire)
```

P-value is less than $0.05$, then reject null hypothesis. Namely, there is a difference is the energy consumption resulted by the activated push API when using different browsers.

**RQ2: Impact of distribution patterns**
